\section{Super Additivity of Quantum Channels}

Superadditivity in quantum information theory refers to the phenomenon where
certain types of quantum capacities increase when multiple channels (or multiple
uses of the same channel) are considered, rather than treating each channel
(or use) independently. This property arises because quantum entanglement and
correlations can enhance the effectiveness of the channel when used in a
collective or joint manner. Superadditivity is a fundamental property that
distinguishes quantum information theory from classical information theory.

This Superadditivity is the result of entanglement and other exotic correlation
phenomena that arises in quantum systems. Superadditivity enhances
communication capabilities of quantum channels and allows more communication
than what their classical counterparts could (sometimes even through
zero capacity channels).

\subsection{Classical Capacity}
One manifestation of superadditivity appears in the classical capacity of quantum
channels, particularly through the Holevo information. As we have seen before, the
Holevo Information of a quantum channel is an upper bound on the classical information
that can be transmitted through it. Also as we have seen before, Classical capacity
has been defined in terms of the Holevo information. As a result, it can exhibit
superadditivity when multiple channel uses are considered together. For example, when
encoding information across multiple uses of the channel in an entangled way or by
using complex encoding schemes, the total classical capacity often exceeds what would be
achievable by simply using each channel separately. Thus, superadditivity allows us to
exploit collective encoding and decoding strategies to maximize the amount of classical
information extracted from quantum channels.

Although it is worth noting that we don't yet know the precise mathematics behind why
Holevo information is superadditive, we just know from counter examples that additivity
is not the general case and super additivity can exist.

Mathematically, we write the Holevo information of two channels acting in parallel as:
\begin{equation}
    \chi(\mathcal{N} \otimes \mathcal{M}) \geq \chi(\mathcal{N}) + \chi(\mathcal{M})
\end{equation}
Now, since classical capacity is:
\begin{equation}
    C(\mathcal{N}) = \lim_{n \rightarrow \infty }\frac{1}{n}\chi(\mathcal{N}^{\otimes n})
\end{equation}
For channel $\mathcal{N}\otimes\mathcal{M}$ we have:
\begin{align}\begin{split}
    C(\mathcal{N}\otimes\mathcal{M}) & = \lim_{n \rightarrow \infty }\frac{1}{n}\chi[(\mathcal{N}\otimes\mathcal{M})^{\otimes n}]\\
    & \geq \lim_{n \rightarrow \infty }\frac{1}{n}[\chi(\mathcal{N}^{\otimes n}) + \chi(\mathcal{M}^{\otimes n})]\\
    & = \lim_{n \rightarrow \infty }\frac{1}{n}\chi(\mathcal{N}^{\otimes n}) + \lim_{n \rightarrow \infty }\frac{1}{n}\chi(\mathcal{M}^{\otimes n})\\
    & = C(\mathcal{N} + \mathcal{M})
\end{split}\end{align}
As the math clearly demonstrates, the Classical capacity is superadditive as a consequence
of the superadditivity of the Holevo information.

\subsection{Quantum Capacity}
The concept of superadditivity is particularly important when discussing the quantum capacity
of a channel, which measures the maximum rate at which quantum information can be transmitted
reliably. Similar to classical capacity, quantum capacity does not exhibit simple additivity;
instead, two or more uses of a channel can yield an overall capacity greater than the sum of
the individual capacities. This phenomenon is linked to the coherent information of the
channel, similar to how the classical capacity is linked to the Holevo Information of a channel.
Since coherent information itself can be superadditive, the overall quantum capacity of a
channel may similarly display superadditivity.

Mathematically, we may write this as:
\begin{equation}
    Q(\mathcal{N} \otimes \mathcal{M}) \geq Q(\mathcal{N}) + Q(\mathcal{M})
\end{equation}

One classical analogy would be to consider a system where combining two noisy communication
lines produces a more reliable transmission than would be expected from their individual
performance, but in quantum mechanics, this is achieved by leveraging entanglement and quantum
correlations.

\subsection{Private Capacity}

It is interesting to see that for quantum channels, not only the quantum and classical capabilities
but also the private capacity can be superadditive! As demonstrated by \cite{Li_2009}, there is
possibility for two channels with limited private capacity to combine as a tensor product channel
to have private capacity greater than the sum of the two. We do not know the exact formulation of
this relation as of now, so we write:

\begin{equation}
    P^?(\mathcal{N} \otimes \mathcal{M}) > P^?(\mathcal{N}) + P^?(\mathcal{M})
\end{equation}

The superadditivity of quantum channels is still a pretty unexplored topic, and there are many open
questions still unanswered.